### 2019-12-15 asru_2019_maximizing_uniformity_of_distribution/doc/asru_2019_reviewer_rebuttal.txt

Summary:
We would like to thank all the reviewers for sparing time out of their busy schedule to provide very useful comments on our paper. The major novelty of this paper is that we proposed a new way of deriving a suitable compressive nonlinearty from the data themselves. In case of the previous power-law nonlinearty of 1/15, it was obtained by curve-fitting from the rate-intensity curve of the human auditory system and additionally by performing speech recognition experiments with various power coefficients to find out the best value. These steps require a lot of time for obtaining the best power-coefficient. Because of this problem, we couldn’t fine tune the power coefficient for each filter bank channel when we first presented this work in our previous PNCC paper in 2012 and in 2016. In this new MUD approach, we  obtain suitable coefficients for each filterbank channel “without” actually running speech recognition experiments. This is a huge benefit compared to the previous hand-crafted fine tuning. In addition, we believe that this approach can be extended to other domains like vision. The  previous power coefficient of 1/15 was already hand-optimized by performing experiments with  different parameters. This it is quite natural that the additional improvement over this previous optimized system with a power coefficient of 1/15 is relatively small. However, the major importance of this work is that we proposed a new way of designing the compressive nonlinearity from data themselves, and this approach is much more flexible and may be extended to other domains as well.

To the reviewer #0D85

First, thank you very for carefully reviewing the paper. We greatly thank your complimentary ratings and giving very helpful comments.
We reply to your comments as follows:

1. About using an external LM.
We recently performed an experiment using a Transformer LM with a shallow-fusion technique. This approach showed around 30 % additional relative improvement in Word Error Rate (WER).  If this paper is accepted, we will include this result as well.

2. About performance improvement over the power-law nonlinearty of 1/15.
It is indeed true that the additional improvement over the previous power coefficient of 1/15 is not  large. However, as mentioned in the summary part of this rebuttal, the importance of this work is that we suggested a completely new way of obtaining the compressive non-linearity. Unlike our previous PNCC paper, we didn’t need to conduct speech recognition experiments with different power-law coefficients to obtain the optimal coefficient. This is a huge benefit compared to the previous hand-crafted fine tuning. In addition, we believe that this approach can be extended to other domains like vision. The  previous power coefficient of 1/15 was already hand-optimized by performing experiments with  different parameters. This it is quite natural that the additional improvement over this previous optimized system with a power coefficient of 1/15 is relatively small. When we come up with the power coefficient of 1/15, we couldn’t optimize the power coefficient for different filter bank channel, since it will take too much time for doing such an experiment. In the new MUD approach, we could easily optimize power coefficient for different filterbank channel very easily using a new criterion. In the future, we believe that this algorithm can be applied to other domains (such as vision) as well.

3. The meaning of “easier”
If the features are difficult to learn, parameter convergence usually becomes more difficult due to the erratic error function surface. In this case, we usually have hard time in fine-tuning learning rates and hyper parameters to obtain converged parameters. In this paper, “easier” means that the neural network may be trained well without too much fine-tuning because of the well-behaved feature distribution and the error surface.

Again, thank you and we really appreciate your complimentary remarks!

To the reviewer #0c9#

First, thank you very much for carefully reviewing the paper. We greatly appreciate your review comments. If this paper is accepted, we will include experimental results obtained using 10,000-hr Bixby training set.
Thank you very much for your complimentary review!

To the reviewer #0DF3.

First, thank you very much for carefully reviewing the paper. We greatly appreciate your review comments. Thank you for mentioning the Spec-Augment paper. We checked that spec-Augment shows better performance. Once this paper is accepted, we will modify the content mentioning that this is the best result without using data-augmentation. After submitting this work, we could reduce WER  relatively by 30% by using a transformer LM.

To the reviewer #0D3A

First, thank you very for carefully reviewing the paper. We greatly thank your complimentary ratings and giving very helpful comments.
We reply to your comments as follows:

1. About performance improvement over the power-law nonlinearty of 1/15.
It is indeed true that the additional improvement over the previous power coefficient of 1/15 is not  large. However, as mentioned in the summary part of this rebuttal, the importance of this work is that we suggested a completely new way of obtaining the compressive non-linearity. Unlike our previous PNCC paper, we didn’t need to conduct speech recognition experiments with different power-law coefficients to obtain the optimal coefficient. This is a huge benefit compared to the previous hand-crafted fine tuning. In addition, we believe that this approach can be extended to other domains like vision. The  previous power coefficient of 1/15 was already hand-optimized by performing experiments with  different parameters. This it is quite natural that the additional improvement over this previous optimized system with a power coefficient of 1/15 is relatively small. When we come up with the power coefficient of 1/15, we couldn’t optimize the power coefficient for different filter bank channel, since it will take too much time for doing such an experiment. In the new MUD approach, we could easily optimize power coefficient for different filterbank channel very easily using a new criterion. In the future, we believe that this algorithm can be applied to other domains (such as vision) as well.

2. About the statistical significance of the improvement over the previous power-law coefficient of 1/15.
 For the Libri speech test-other, we checked that the WER difference is statistically significant.

### 2019-12-16 asru_2019_training_infra/poster/main.tex
Update the poster

\begin{minipage}[t]{1.0\linewidth}
\begin{center}
  \begin{minipage}[t]{0.1\textwidth}
    \centering
    \vspace{0pt}
    \includegraphics[width=10cm, valign=t]{samsung_research} % Logo or a photo of you, adjust its dimensions here
  \end{minipage} \hfill
  \begin{minipage}[t]{0.7\textwidth}
    \begin{center}
  \huge \color{NavyBlue} 
      \textbf{Power-law nonlinearity with maximally uniform distribution criterion for
      improved neural network training in automatic speech recognition} \\
      \LARGE \textbf{Chanwoo Kim, Mehul Kumar, Kwangyoun Kim, and Dhananjaya Gowda}
  \\
\LARGE Samsung Research, Seoul, South Korea\\ % University/organization
\large \{chanw.com, mk0211.shin, ky85.kim, d.gowda\}@samsung.com
    \end{center}
  \end{minipage}
  \begin{minipage}[t]{0.1\textwidth}
    \begin{center}
    \includegraphics[width=10cm]{samsung_research} % Logo or a photo of you, adjust its dimensions here
    \end{center}
  \end{minipage} \hfill
\end{center}
\end{minipage}
%
%\begin{minipage}[b]{0.25\linewidth}
%\color{DarkSlateGray}\Large \textbf{Contact Information:}\\
%Department Name\\ % Address
%University Name\\
%123 Broadway, State, Country\\\\
%Phone: +1 (000) 111 1111\\ % Phone number
%Email: \texttt{john@LaTeXTemplates.com}\\ % Email address
%\end{minipage}
%

\vspace{1cm} % A bit of extra whitespace between the header and poster content

@@

@@

%----------------------------------------------------------------------------------------
%	ABSTRACT
%----------------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

@@

\section{Motivation}

\begin{enumerate}
  \item Applies Vocal Tract Length Perturbation (VTLP) to diversify the
    training database \cite{n_jaitly_icml_workshop_2013_00}.
  \item Resynthesizes VTLP-processed waveforms before performing feature extraction.
    \begin{itemize}
        \item We can apply the acoustic simulator after performing the VTLP
          processing.
        \item We may use a different window length for the frequency warping from
          the one used in feature processing for performance optimization.
    \end{itemize}
\end{enumerate}

\color{DarkSlateGray} % DarkSlateGray color for the rest of the content
  \section{Maximization of Distribution Uniformity}

\begin{Figure}
  \begin{center}
    {
      \includegraphics[width=170mm]{mel_filterbank_energy_histogram}
      \label{fig:mel_filterbank_energy_histogram}
    }   
    \\  
    {
      \includegraphics[width=170mm]{power_function_based_mud_output_histogram}
      \label{fig:power_function_based_mud_output_histogram}
    }   
  \vspace{-2mm}
    \\  
    {
      \includegraphics[width=170mm]{histogram_based_mud_output_histogram}
      \label{fig:histogram_based_mud_output_histogram}
    }   
  \vspace{-2mm}
    \captionof{figure} {
      The Probability Density Functions for the third filterbank channel
       of (a): the mel filterbank energy $p[m, l], l = 3$ in  
       \eqref{eq:mel_filterbank_energy}, (b): the power-function based MUD 
      output of this mel filterbank energy in \eqref{eq:power_mud}, (c) 
      the histogram based-MUD in \eqref{eq:histogram_mud}. 
      \label{fig:pdf_mud}
    }   
   \vspace{-7mm}
  \end{center}
\end{Figure}

%\begin{center}
%  \includegraphics[width=0.2\linewidth]{power_function_based_mud_output_histogram}

%\captionof{figure}{
%  \label{fig:bilinear_transform}
%      The relation between the input frequency and the
%      warped frequency using the bilinear transformation
%      \eqref{eq:bilinear_transformation}.}
%
%\end{center}

%\item \textbf{IFFT and OverLap Addition (OLA)} Re-synthesize the waveform.
%\end{enumerate}

%\begin{figure}%[!tbp]
%\end{figure}

\section{End-to-End Speech recognition}

\begin{minipage}{1.0\linewidth}
  {
    \normalsize
  \begin{center}
  \resizebox{180mm}{!}{\input{../figures/e2e_asr_block_diagram_poster.tex}}
  \end{center}
\captionof{figure}{ 
  The structure of the entire end-to-end speech recognition system.}
  }
\end{minipage}

  We used the RETURNN speech recognition system
  \cite{a_zeyer_interspeech_2018_00} with various modifications:
    \begin{itemize}
      \item{Gradient clipping and learning-late warm-up.}
      \item{Power-mel feature} Motivated by the power-law nonlinearity of ($(\cdot)^{\frac{1}{15}}$) in PNCC \cite{C_Kim_IEEETran_2016_1}.
      \item{Modified shallow fusion with a Transformer LM}

        \begin{align}
  y_{0:L}^{*} = & \argmax_{y_{0:L}} \sum_{l=0}^{L-1} \Big[ \log P \left(y_l
  |\vec{x}[0:M], y_{0:l} \right)
  \nonumber \\
                           & \qquad - \lambda_p \log P(y_l)
                           + \lambda_{\text{lm}} \log P \left(y_l   |y_{0:l} \right)  \Big],
                           \label{eq:lm_fusion}
\end{align}

@@

%----------------------------------------------------------------------------------------
%	OBJECTIVES
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	MATERIALS AND METHODS
%----------------------------------------------------------------------------------------

\section{Experimental Results}
\begin{itemize}
  \item For training, we used { \bf the Librispeech train-clean and
    train-other}.
  \item For evaluation, we used { \bf the test-clean and test-other of this Libri
    Speech database. }
\end{itemize}

\begin{minipage}[b]{1.0\linewidth}
  %\begin{table*}[!htbp]
  \renewcommand{\arraystretch}{1.3}
  \centering
      \captionof{table}{\label{tbl:result}
      Word Error Rates (WERs) obtained with MFCC, Power Mel filterbank
      coefficients,  power function-based MUD processing, and
      histogram-based MUD Processing on the LibriSpeech corpus
      \cite{v_panayotov_icassp_2015_00}. 
      }
      %\vspace{-3mm}
      \begin{tabular}{| c | c  || c | c | c | c |}
        \hline
        \multicolumn{2}{| l ||}{Neural Network Structure}
                               & \specialcell{MFCC}
                               & \specialcell{$ ( \cdot ) ^ {\frac{1}{15}}$}
                               & \specialcell{Power Function- \\ Based MUD}
                               & \specialcell{Histogram- \\ Based MUD}   \\
        \hline \hline
        \multirow{3}{*}{\specialcell{1024 cell \\ ULSTM \\ MoCha}}
                & test-clean  &   7.09  \% & \textcolor{blue}{\textbf{ 7.04 }} \%   &   7.10 \%  &  7.13 \%  \\
                & test-other  &  20.60  \% & 19.76 \%
                &  \textcolor{blue}{\textbf{19.64}} \%  & 20.03 \%  \\
                & average     &  13.85  \% & 13.40 \%
                &  \textcolor{blue}{\textbf{13.37}} \%  & 13.58 \%  \\
        \hline \hline

            \multirow{3}{*}{\specialcell{1536 cell \\ BLSTM \\ Full-Attention}}
                & test-clean  &   4.06  \% & \textcolor{blue}{\textbf{3.94}} \%   &   4.02 \%  &  4.11 \%  \\
                & test-other  &  13.97  \% & 13.56 \%
                & \textcolor{blue}{\textbf{13.34}} \%  & 14.10 \%  \\
                & average     &   9.02  \% &  8.75 \%
                & \textcolor{blue}{\textbf{8.68}} \%  &  9.11 \%  \\
        \hline
     \end{tabular}
     \vspace{-4mm}
\end{minipage}
 %----------------------------------------------------------------------------------------
%	REFERENCES
%----------------------------------------------------------------------------------------

@@

%
\color{SaddleBrown} % SaddleBrown color for the introduction
\section{Conclusions}
%
{ \color{red}
We achieved 2.44 \% WER and 8.29 \% WER
  on the Librispeech {\it test-clean} and {\it test-other} databases.
To the best of our knowledge, the 2.44 \% WER on the {\it test-clean}
is the best result ever reported on this database
}
%
%
\begin{enumerate}
  \item Applies Vocal Tract Length Perturbation (VTLP) to diversify the
    training database. \cite{n_jaitly_icml_workshop_2013_00}
  \item Resynthesizes VTLP-processed waveforms before performing feature extraction.
    \begin{itemize}
        \item We can apply the acoustic simulator after performing the VTLP
          processing.
        \item We may use a different window length (50 {\it ms}) for the frequency warping from
          the one used in feature processing (25 {\it ms}).
    \end{itemize}
  \item Applies the power-mel feature.
  \item Applies a modified shallow-fusion with a Transformer LM.
\end{enumerate}
\color{DarkSlateGray} % DarkSlateGray color for the rest of the content
%----------------------------------------------------------------------------------------
\bibliographystyle{IEEEtran}
\bibliography{../../common_bib_file/common_bib_file}
\end{multicols}
\end{document}

>>>>

\begin{minipage}[t]{1.0\linewidth}
\begin{center}
  \begin{minipage}[t]{0.1\textwidth}
    \centering
    \vspace{0pt}
    \includegraphics[width=10cm, valign=t]{samsung_research} % Logo or a photo of you, adjust its dimensions here
  \end{minipage} \hfill
  \begin{minipage}[t]{0.79\textwidth}
    \begin{center}
  \huge \color{NavyBlue} 
      \textbf{End-to-end Training of a Large Vocabulary \\ End-to-end Speech Recognition System
      } \\
      \Large \textbf{
      Chanwoo Kim, Sungsoo Kim, Kwangyoun Kim, Mehul Kumar,  Jiyeon Kim, \\ 
      Kyungmin Lee, Changwoo Han, Abhinav Garg, Eunhyang Kim,  \\ 
      Minkyoo Shin, Shatrughan Singh, Larry Heck, Dhananjaya Gowda
      }
  \\
\Large Samsung Research, Seoul, South Korea\\ % University/organization
{ \large \tt  \{chanw.com, ss216.kim, ky85.kim, mehul3.kumar, jstacey7.kim,} \\ 
  \large \tt  {k.m.lee, cw1105.han, abhinav.garg, sc.ehkim.jin,} \\
  \large \tt  {mk0211.shin, shatrughan.s, larry.h, d.gowda\}@samsung.com }
    \end{center}
  \end{minipage}
  \begin{minipage}[t]{0.1\textwidth}
    \begin{center}
    \includegraphics[width=10cm]{samsung_research} % Logo or a photo of you, adjust its dimensions here
    \end{center}
  \end{minipage} \hfill
\end{center}
\end{minipage}
%
%\begin{minipage}[b]{0.25\linewidth}
%\color{DarkSlateGray}\Large \textbf{Contact Information:}\\
%Department Name\\ % Address
%University Name\\
%123 Broadway, State, Country\\\\
%Phone: +1 (000) 111 1111\\ % Phone number
%Email: \texttt{john@LaTeXTemplates.com}\\ % Email address
%\end{minipage}
%
%
\vspace{-2mm} % A bit of extra whitespace between the header and poster content
%

@@

%

@@

%
%	ABSTRACT
%
%

@@

%
%	INTRODUCTION
%

@@

%
\section{Summary}
%
\begin{itemize}
\item Achieves the state of the art speech recognition performance for commercial products using an end-to-end pipeline that performs all of data reading,  large scale data augmentation \cite{c_kim_interspeech_2019_00}, power-mel feature extraction \cite{c_kim_asru_2019_00}, and  distributed neural network parameter updates in an “on-the-fly” way.
\item Performs Vocal Tract Length Perturbation and Acoustic Simulation \cite{C_Kim_INTERSPEECH_2017_1} on the CPU queue using example servers.
\item Performs Neural Beamforming \cite{j_heymann_icassp_2016_00} on the device side for further improvement in far-field noisy environments.
\item Performs experiments both using the on-line MoCha \cite{k_kim_asru_2019_00} and the Bidirectional Full-Attention (BFA) approach.

@@

%
%
\color{DarkSlateGray} % DarkSlateGray color for the rest of the content
  \section{Overall Structure}
The overall structure is shown in Fig. \ref{fig:end_to_end_training_system}
\begin{itemize}
\item \textbf{Data reading}: Using sharded {\tt TFRecords} and {\tt tf.data}.
\item \textbf{Data augmentation and feature extraction}: VTLP, AS, and power-mel feature extraction are running on the example servers.
\item \textbf{Connection between the example servers and the GPU servers}: Using {\tt ZeroMQ} for asynchronous message queueing.
\item \textbf{Distributed neural net training}: Training on the GPU server using {\tt horovod}.
%
%
\begin{Figure}
  \begin{center}
    \resizebox{\textwidth}{!}{\input{../figures/end_to_end_training_system_poster.tex}}
      \captionof{figure} { The Samsung Research end-to-end training framework for building an end-to-end
  speech recognition system with multi CPU-GPU clusters and on-the-fly data
  processing and augmentation pipeline.
     }
     \label{fig:end_to_end_training_system}
  \end{center}
\vspace{-5mm}
\end{Figure}
%
%
%
%
\begin{minipage}[]{0.45\linewidth}
  {
    \normalsize
  \begin{center}
  \resizebox{120mm}{!}{\input{../figures/e2e_asr_block_diagram_poster.tex}}
  \end{center}
\captionof{figure}{ 
  The neural network structure for end-to-end speech recognition.}
  }
\end{minipage}
%
%
\begin{minipage}[]{0.54\linewidth}
  We used the RETURNN speech recognition system \cite{a_zeyer_interspeech_2018_00} with various modifications:
    \begin{itemize}
      \item{MoCha\cite{k_kim_asru_2019_00} and the modified beam search decoder.}
      \item{Gradient clipping, modified learning-late warm-up, and so on.}
      \item{Power-mel feature} Motivated by the power-law nonlinearity of ($(\cdot)^{\frac{1}{15}}$).
      \item{Modified shallow fusion with a Transformer LM \cite{c_kim_interspeech_2019_00}}
        \begin{align}
  y_{0:L}^{*} = & \argmax_{y_{0:L}} \sum_{l=0}^{L-1} \Big[ \log P \left(y_l
  |\vec{x}[0:M], y_{0:l} \right)
  \nonumber \\
                           & \qquad - \lambda_p \log P(y_l)
                           + \lambda_{\text{lm}} \log P \left(y_l   |y_{0:l} \right)  \Big],
                           \label{eq:lm_fusion}
\end{align}
    \item{Example queues for efficient data augmentation}
\end{minipage}
%
%
\begin{Figure}
  \captionsetup[subfigure]{justification=centering}
    \centering
    \begin{minipage}{0.49\linewidth}
			\centering
      {\includegraphics[width=175mm]{../figures/plot_example_server_time}  \label{fig:plot_example_server_time} }
			{(a)}	
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
			\centering
      {\includegraphics[width=175mm]{../figures/plot_gpu_time_percentage} \label{fig:plot_gpu_time_percentage} }
			{(b)}	
    \end{minipage}
  \captionof{figure} {\label{fig:plot_example_server_performance}
  The efficiency of the {\it example server} with respect to
  the number of CPUs per GPU: (a) The required time to
  process a single epoch during the training phase and (b)
  the percentage of {\tt Tensorflow } computation time defined by
  $t_{\text{session}} =  \frac{\text{Time Spent in {\tt Tensorflow}
  Session}}{\text{Elapsed Time}}$.
  The blue horizontal dotted lines in each figure represent the case
  when data augmentation with example servers is not employed.
  }
\end{Figure}
%
%
\section{Experimental Results}
%
%
%
%
\begin{itemize}
\item \textbf{LibriSpeech experiments} (960-hr training and evaluation on 5.4-hr LibriSpeech {\tt test-clean}) \\
\begin{minipage}[b]{1.0\linewidth}
%\begin{table}[!tbhp]
  \renewcommand{\arraystretch}{1.3}
  \centering
        \captionof{table}{\label{tbl:near_field_result}
        Summary of Word Error Rates (WERs) obtained for different
        LibriSpeech and {\tt Bixby } near-field end-to-end ASR models
        with and without an RNN LM.
        }
        %\vspace{-3mm}
        \begin{tabular}{| c | c  || c | c |}
          \hline
          \multicolumn{2}{| l ||}{Models}
                                 & BFA
                                 & MoChA \\
          \hline \hline
          \multirow{3}{*}{\specialcell{LibriSpeech \\ (1536-cell) \\ test-clean}}
                  & w/o LM  &   3.66  \% &  6.78  \%  \\
                  & RNN-LM  &   2.85  \% &  5.54  \%  \\
                  & Transformer LM  &   2.44  \% &   -   \\
          \hline
          \multirow{2}{*}{\specialcell{Bixby \\ (1024-cell) }}
                  & w/o LM  &   8.25  \% &  10.77  \% \\
                  & RNN-LM  &   7.92  \% &   9.95  \% \\
          \hline
       \end{tabular}
       \vspace{-2mm}
%\end{table}
\end{minipage}
%
%
%
%
\begin{itemize}
\item \textbf{Bixby English command-set experiments} (10,000-hr {\tt Bixby } training set and {\tt Bixby} command test sets) \\
\item Note that the MoCha version of the system trained using  {\tt Bixby } training set was commercialized for on-device dictation for high-end Samsung mobile phones. \\
\begin{Figure}
  \captionsetup[subfigure]{justification=centering}
    \centering
    \begin{minipage}{0.49\textwidth}
			\centering
      {\includegraphics[width=175mm]{../figures/plot_farfield_wer_tv}}
			{(a)}	
    \end{minipage}
%
    \begin{minipage}{0.49\textwidth}
			\centering
      {\includegraphics[width=175mm]{../figures/plot_farfield_wer_music}}
		{(b)}
    \end{minipage}
%
%
  %\vspace{-6mm}
 \captionof{figure} {\label{fig:plot_farfield_wer}
  Speech recognition accuracy at different Signal-to-Noise Ratios (SNRs)
  under three different noisy conditions: direct TV noise (a)
  , music noise (b), and babble noise (c). NBF, VTLP, and AS
  stand for Neural Beam Former (NBF) \cite{j_heymann_icassp_2016_00},
  Vocal Tract Length Perturbation (VTLP) \cite{c_kim_interspeech_2019_00} , and
  Acoustics Simulator (AS) \cite{c_kim_interspeech_2017_00},
  respectively.
  \vspace{-2mm}
 }
\end{Figure}
%	REFERENCES

@@

%
\color{SaddleBrown} % SaddleBrown color for the introduction
%\section{Conclusions}
%%
%\begin{enumerate}
%\item We achieved 2.44 \% WER and 8.29 \% WER
%  on the Librispeech {\it test-clean} and {\it test-other} databases.
%%
%\end{enumerate}
%
\color{DarkSlateGray} % DarkSlateGray color for the rest of the content
%----------------------------------------------------------------------------------------
\small
\bibliographystyle{IEEEtran}
\bibliography{../../common_bib_file/common_bib_file}
\end{multicols}
\end{document}
